Distant Suns for JWST Flux Calibration

### 2019-04-11 ms.tex
added color-magnitude diagrams with near-G2 Vs labeled.
started modifying the title to focus on faint G2V solar analogs
got rid of flux ladder stuff and made edits to first few pages.

\shorttitle{NIRCam Flux Calibration}
\shortauthors{Schlawin et al.}

@@

\title{NIRCam Faint and Bright Flux Calibration Plan}

@@

\author{E. Schlawin, G. Rieke, Jarron Leisenring, M. Rieke, K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

@@

\altaffiltext{1}{Hubble Postdoctoral Fellow}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals.
One area where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe.
JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.

@@

The original flux calibration effort has mainly bright stars ($K \lesssim 15$).
Example spectra for these calibrators are shown in Figure \ref{fig:JWSTcalsWideF} with saturation and sensitivity limits of NIRCam's wide filters.
Many of these spectra will saturate the NIRCam detectors when used in full frame (shown as the middle parts of the black ``error bars'') for wide-band filters.
Furthermore, there may be systematic errors when observing faint targets and low detector well depths.
As an example of a systematic detector effect, consider charge traps within a detector.
These traps would tend to decrease the measured number of electrons per second on the first exposure because they would trap electrons  that would not be read out by an amplifier.
For bright sources, the effect of the traps would be smaller since they would quickly be a small fraction of the flux.
For faint sources, however, the traps would be a larger fraction of the incoming electrons.
Therefore, the charge traps (if not corrected for) would tend to decrease the flux of faint sources as compared to bright targets.

@@

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band. This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.15 mag.
Thus, to calibrate all wide band filters in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.95.
\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module).
We selected clusters with WEBDA diameters $\lesssim 15\arcmin$
\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
\item {\bf Visibility} The clusters should be spread out in ecliptic longitude to ensure that at least one is visible during the commissioning period.
\end{itemize}

With all these considerations in play, we selected NGC 2420 as the best fit for the multiple criteria.
The only parameter that is not satisfied is the distance modulus, so additional sources or conversions are needed for the F070W, F090W, F115W and F150W filters.
At the time NGC 2420 was selected, the JWST throughputs were smaller than the measured values so it saturated fewer filters.
One way to calibrate these short wavelength, wide filters is to use subarrays.
The subarray to full frame conversion can be checked with medium band filters.
NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.05 $\le$ [Fe/H] $\le$ 0.04.
NGC 2506, is metal poor at [Fe/H]=-0.32, so corrections must be made for changes to G2 V spectra due to metallicity.

@@

@@

\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event as the reference sphere.

\begin{figure}[!t]
\centering
\includegraphics[width=.8\columnwidth]{flux_ladder.pdf}
\caption{Schematic sensitivity ladder going from an MSX standard (with a sub-array, neutral density filter observation) to a faint JWST standard (with a full array, full throughput observation).
Each observation step is labeled in the bottom corner of each image schematic.
An intermediate standard (shown with green connecting arrows) can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
\end{figure}

\begin{table}[!b]
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:conversionSteps}
\begin{tabular}{lrrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& $K_\mathrm{src}$		& ND Square		& Subarray	& Filter & t$_\mathrm{exp} (s) $ &$K_\mathrm{sat}$\\
\hline \hline
1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 & -4.0 \\
2		& Bright JWST Calibrator			& A0 V, G2 V		& 6.5	  		& On &	64$\times$64	& F430M &  220 & -4.0 \\
3		& Bright JWST Calibrator			& G2 V			& 6.5  		& Off &	64$\times$64	& F430M &  0.1 & 6.2 \\
4		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 & 6.2 \\
5		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 & 12 \\
6		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 & 13.7 \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A. The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp. The saturation limit is at 80\% well depth for 2 non-destructive reads up the ramp following a reset.}
\vspace{0.05in}
\end{table}

\begin{table}[!b]
\centering
\caption{Example Stars for Each Calibrator Step.}\label{tab:stepStars}
\begin{tabular}{lrrr}
\hline \hline
Step	(s)	& Source						& Spectral Type	& $K_\mathrm{src}$\tablenotemark{a}	\\
\hline \hline
1		& $\alpha$ Cen (Sirius)			& A1 V 			& -1.35		\\
1		& $\gamma$ Dra (Eltanin)			& K5 III 			& -1.35		\\
1		& $\alpha$ Lyr (Vega)			& A0 V 			& 0.13		\\
2 - 3		& HD 37962					& G2 V			& 6.27	  	\\
2 - 3		& HD 38949					& G1 V			& 6.44	  	\\
4 - 6		& 07:38:17.1 +21:36:22 (NGC 2420)	& G2 V			& 15.6 		\\
\hline
\end{tabular}
\tablenotetext{a}{NOTE, these magnitudes from Simbad may have up to 5\% systematics for steps 1-3..}
\vspace{0.05in} f
\end{table}

Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with MSX calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source (a horizontal move) or a new source is measured with the same instrument configuration (a vertical move).
As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require long integration times so the bright calibrators are preferred for steps 2 and 3.

This bright JWST standard would be used to transfer from the ND filter with a coronagraphic pupil mask to direct imaging.
This conversion step can independently be checked against other instruments' measurements of the bright JWST calibrator, such as by STIS with HST.
The next step would be to use the same direct image configuration and subarray size to observe a faint JWST calibrator around $K \sim$15.
S/N ratios of 200 can be achieved in 94 seconds in this mode.
This calibrator star would now be observable in full frame mode without saturation so the next step would be a conversion from subarray to full frame on the same source.
Since the solar analog flux standards identified in this program are in a cluster, there are many sources available for photometry.
It may be useful to make additional measurements to confirm the subarray to full frame conversion using a concentration of stars in a cluster over a range in magnitude.
To calibrate the wide band filters, such as F444W, one final step would be needed to go from the medium to wide band photometry using a model for the star.
Either a well-characterized white dwarf spectrum of a known standard or a faint G2 V standard from an open cluster would be good models for this transfer of filters.

Table \ref{tab:conversionStep} shows the saturation limits for each mode as well as the

\subsection{Using Intermediate Standards to Check the Flux Ladder}

Figure \ref{fig:sensitivityLadder} shows that an intermediate JWST standard such as P-330 E can be used to check transfers and detector linearity corrections.
The solar analog P330-E is a commonly used standard because of its similarity to the sun.
This step would not be an essential ``rung'' in the NIRCam flux ladder (since it involves more steps) but a useful check on other transfers.

However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to full frame imaging in a narrowband mode in 3 steps by using an intermediate JWST standard.
This shorter ladder is illustrated in Figure \ref{fig:sensitivityLadderP330E}.
To begin, the F212N filter would be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
If the F212N filter is used to image P330-E with a full frame direct imaging mode, it is just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
The F212N filter is chosen since there are few stellar absorption lines in this filter.
The advantage with this single transfer from an MSX standard to a full frame P330-E image is that it fewer steps than the ladder described above.
The disadvantage is that there would be a large disparity in detector well depth between the steps on this ladder.
If flux calibration time is available, this alternative flux ladder or simply the ``offshoot'' would serve as a check on the conversion from faint to bright targets.

\begin{figure}[!t]
\centering
\includegraphics[width=.32\columnwidth]{flux_ladder_p330e.pdf}
\caption{Schematic of an alternative sensitivity ladder to Figure \ref{fig:sensitivityLadder}.
This ladder would use the intermediate-brightness JWST standard P330-E (G2~V type) to transfer from an MSX star to full frame imaging in a narrowband filter.
The observing time needed for step 2 is considerable, but if allocated (7.5 hr to get SNR=200), this provides a way to calibrate full frame imaging with fewer transfers than the 6 step method above.
The disadvantage of this method is that each step involves a large disparity in well depths.
The steps are labeled B1 through B3 do distinguish between these and steps 1-6 in Figure \ref{fig:sensitivityLadder}.}\label{fig:sensitivityLadderP330E}
\end{figure}

\subsection{Ways to Observe Bright Stars}\label{sec:brightStarMode}

There are several ways to improve saturation limits with NIRCam over direct imaging:
\begin{itemize}
\item \textbf{Lyot Stop} Cut down the aperture size with a Lyot stop. These have 19\% throughput (1.8 mags). Additionally, this broadens the PSF - see Figure \ref{fig:psfComparison}.
The broadening spreads light out by a similar factor (contributing 1.8 mags to saturation limits) for a total of 3.5 mags.
\item \textbf{Neutral Density Square} The neutral density filters have an attenuation of 10$^3$ or 7.5 mags. A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
Additionally, the Lyot stop must be in place to use the neutral density filter so the total improvement on saturation limits is 11 mags over direct imaging.
Care must be taken with dithering to ensure that non-uniform optical depth of the neutral density filter doesn't affect the photometry.
\item \textbf{Grisms} For long wavelength NIRCam observations ($2.4~\mu$m$ > \lambda < 5~\mu$m), one can use a grism to spread out the light. This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter and 2048$\times$64 subarray \citep{greene2016wfss}, which does not reach to the MSX standards.
This could be potentially combined with the coronagraphic pupil, but this combination has not been tested or explored in detail.
One could potentially observe small pieces of the spectrum at a time with a subarray that are all combined to create a spectrum, but this would add time and may be difficult to implement.
\item \textbf{DHS} For short wavelength NIRCam spectra ($1.0~\mu$m$ > \lambda < 2.0~\mu$m), one can use the Dispersed Hartmann Sensor. The dispersed Hartmann Sensor (DHS) reduces the pupil throughput and spreads the light out to reach saturation limits of $K$=0.2 to 1.5 depending on spectral type \citep{schlawin2017dhs} for a 2048$\times$64 subarray.
This is not bright enough to observe the MSX calibrators.
As with the long wavelength grisms, one would have to read small subarrays (e.g. 64$\times$64) to get to brighter limits.
If one stitched together a spectrum from these subarrays along the spectrum, this could theoretically be used on all MSX stars.
However, as with the grism mode above, there would be significant changes and additions to the flight software to implement a mode that would build a spectrum out of 32 different subarrays.
\item \textbf{Extra Small Subarrays} There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray.
There may be complications with calculating accurate integration times in this mode because any uncertainties affecting a frame time could be a significant fraction of the $\sim$ 2 ms frame time.
The background annulus would be limited for such small subarrays.
\item \textbf{Weak Lens} The Weak Lenses spread light out over many pixels which can be helpful for bright stars. However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out the effect of spreading the light out over many pixels.
For a very narrowband filter such as F212N, the K-band saturation limit for a weak lens observation with a 128$\times$128 subarray is 0.9 mag (Vega mag) for a G2V star, which does not quite reach the MSX calibrators.
\end{itemize}

Of the many options here, the most feasible method is the neutral density square with the Lyot Coronagraphic pupil mask.
Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with either Phoenix stellar models \citep{allard2012phoenix} or \citet{castelli2004models} models.

\subsection{Observing MSX Stars}

Observing the MSX flux standards (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}\footnote{https://github.com/JarronL/pynrc.git}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.

\subsubsection{Complications with PSF}
A Lyot pupil mask must be used when imaging through the neutral density squares since the wedges that redirect light through NIRCam's coronagraphic masks and neutral density squares are co-located with the Lyot stop pupil masks.
In addition to lowering the transmission by a factor of 19\%, the Lyot stops spread out the PSF as compared to direct imaging.
Figure \ref{fig:psfComparison} shows example PSFs calculated with \texttt{webbpsf} \citep{perrin2012webbpsf}.
Figure \ref{fig:psfDirect} shows the direct image PSF versus the the coronagraphic PSF (Figure \ref{fig:psfND}), both normalized to the peak pixel.

When using the ND filter and Lyot stop, the aperture photometry must account for the large secondary peaks of the PSF.
This can be accomplished with a large aperture covering all the secondary peaks assuming that the background levels are low and that there are no nearby sources.
Alternatively, one could extract the flux from the core of the PSF.

\begin{figure*}
\centering
\subfloat[Direct Imaging PSF]{
	\includegraphics[width=0.45\textwidth]{psf_direct.pdf}
	\label{fig:psfDirect}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.45\textwidth]{psf_ND.pdf}
	\label{fig:psfND}
	}
	\caption{The \texttt{webbpsf} direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop. Both images are normalized by the peak pixel value and have arbitrary array positions but the same height and width. Aperture photometry of the sources imaged through the coronograph will have to use a large aperture encompassing the 6 outer peaks or just use the central peak(s) and apply careful background subtraction. Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.\vspace{0.05in}}
	\label{fig:psfComparison}
\end{figure*}

\subsubsection{Complications with Flat Fielding}
The ND filters are not uniform spatially.
Correcting for any pinholes or blemishes in the ND square surface will likely dominate the error budget for the ND square absolute calibration.
Positioning the sources consistently on the same pixel locations and using the same dither patterns will help with these errors.
The dithers can be used to check the surface irregularities.

\subsubsection{Clocking Issues for Small Subarrays}

Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
Jarron explained further on April 24, 2017.
This is a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
The bug creates extra line overheads on small subarrays.
For example, for a 32$\times$32 subarray, there are sometimes 2 line overheads and sometimes 3 line overheads about $\sim$40/60 \% of the time.
Tony Magoncelli has found a way to deterministically predict when these extra frame times will occur.
However, JWST will not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
For a 64$\times$ 64 subarray, there are almost always 2 line overheads.
At a rate of about 5/8000 frames of test data, there were 3 line overheads.
So, in the worst case unlucky scenario with 64$\times$64 subarray data in RAPID mode with 2 groups up the ramp, there could be an extra 1/64 or 1.6 \% increase in the slope due to the ASIC micro code.
Given that 64$\times$64 frame time is only 0.05 s long, you could easily include hundreds of frames to average out the frame time issue with almost no change in efficiency since JWST acquisition, exposure and dithering overheads would be a much larger fraction of the time.
I would estimate this would have less than 0.01\% of an effect on flux calibration.

>>>>

\shorttitle{Distant Suns}
\shortauthors{Schlawin et al.}

@@

\title{Distant Suns for JWST Flux Calibration}

@@

\author{E. Schlawin, G. Rieke, Christopher Willmer, Jarron Leisenring, M. Rieke, K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

@@

%\altaffiltext{1}{Hubble Postdoctoral Fellow}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals.
One area where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe \citep[e.g.][]{narayan2016wdnetwork,betoule2014cosmologySN}.
For exoplanet host stars in the era of Gaia distances, absolutely calibrated photometry is used to make precision measurements of stellar radii, which in turn give high precision planet radii.
For exoplanet host stars in the era of Gaia distances, absolutely calibrated photometry is used to make precision measurements of stellar radii, which in turn give high precision planet radii \citep[e.g.][]{stassun2017gaiaRadiiMasses}.
JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.

@@

The original flux calibration effort has mainly bright stars ($K \lesssim 15$).
Example spectra for these calibrators are shown in Figure \ref{fig:JWSTcalsWideF} with saturation and sensitivity limits of NIRCam's wide filters.
Many of these spectra will saturate the NIRCam detectors when used in full frame (shown as the middle parts of the black ``error bars'') for wide-band filters.
The 
Furthermore, there may be systematic errors when observing faint targets and low detector well depths.
As an example of a systematic detector effect, consider charge traps within a detector.
These traps would tend to decrease the measured number of electrons per second on the first exposure because they would trap electrons  that would not be read out by an amplifier.
For bright sources, the effect of the traps would be smaller since they would quickly be a small fraction of the flux.
For faint sources, however, the traps would be a larger fraction of the incoming electrons.
Therefore, the charge traps (if not corrected for) would tend to decrease the flux of faint sources as compared to bright targets.

@@

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of F-type stars that would have similar colors to solar analogs.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated wide band filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band.
While the F150W2 ``double-wide'' filter is more easily saturated than F090W, this is filter is unlikely to be used on faint Galaxies because (someone from deep field prog remind me?).
This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.15 mag.
Thus, to calibrate all wide band filters longer than F200W in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.95.
\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module).
We selected clusters with WEBDA diameters $\lesssim 15\arcmin$
\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
\item {\bf Visibility} The clusters should be spread out in ecliptic longitude to ensure that at least one is visible during the commissioning period.
\end{itemize}

With all these considerations in play, we selected NGC 2420 and NGC 2506 as the best fit for the multiple criteria.
The only parameter that is not satisfied by NGC 2420 is the distance modulus, so additional sources or conversions are needed for the F070W, F090W, F115W and F150W filters.
At the time NGC 2420 was selected, the JWST throughputs were smaller than the measured values so it saturated fewer filters.
One way to calibrate these short wavelength, wide filters is to use subarrays.
The subarray to full frame conversion can be checked with medium band filters.
NGC 2506 is the next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.05 $\le$ [Fe/H] $\le$ 0.04.
NGC 2506, is metal poor at [Fe/H]=-0.32, so corrections must be made for changes to G2 V spectra due to metallicity.

@@

\begin{figure*}[!t]
\centering
\subfloat[NGC 2420]{
	\includegraphics[width=0.5\textwidth]{colormag_NGC_2420_near_G2_V.pdf}
	\label{fig:cmdNGC2420nearG2V}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.5\textwidth]{colormag_NGC_2506_near_G2_V.pdf}
	\label{fig:cmdNGC2506nearG2V}
	}
\\
\subfloat[NGC 6811]{
	\includegraphics[width=0.5\textwidth]{colormag_NGC_6811_near_G2_V.pdf}
	\label{fig:cmdNGC6811nearG2V}
	}
	\caption{Color-magnitudes of the three clusters with the near-solar stars identified from spectra.
	}
	\label{fig:cmdPSnearG2V}
\end{figure*}

@@
